\documentclass{main}

\begin{document}

\h{CURRICULUM VITAE OF BENJAMIN GLITSOS}

\begin{center}
    \href{tel:0413-388-191}{0413-388-191} \textbar{} \href{mailto:benglitsos@gmail.com}{benglitsos@gmail.com} \textbar{} \href{www.linkedin.com/in/bglitsos}{www.linkedin.com/in/bglitsos} \textbar{} Connells Point NSW 2221
\end{center}

\hh{Summary}

\begin{center}
    Three years' experience in project and account management and web development. Skilled in written and verbal communication and driven by a strong passion for technology.
\end{center}

\hh{Experience}

\begin{flushleft}

    \details{\textit{Account Manager \& Web Developer}}{\nobreak{Aug 2018 -- Sep 2020},\\\nobreak{\textit{Tonic The Agency}}}

    \begin{itemize}
    \item Business analysis and requirements gathering of an information system of an ASX50 company.
    \item Project management of large-scale web developments along with ERP integration.
    \item Timelining and resourcing using Agile and Waterfall methodologies (Microsoft Project et al).
    \item Managed the entire development life cycle (SDLC) from scoping to quality assurance.
    \item Wrote software documentation and provided technical support to clients.
    \item Conducted market research and technical research and wrote reports for stakeholders.
    \item Contributed to complex UX storyboarding, such as for a product selector of over 300,000 items.
    \item Consistently met deadlines in a fast-paced agency environment with numerous responsibilities.
    \item Web development using SQL, Git, Javascript and Node.js, various APIs, Postman et al.
    \item The digital account manager for four major clients of the agency, having managed over \$1mil in spend.
    \end{itemize}

    \details{\textit{Web Developer}}{\nobreak{Jul 2018 -- Dec 2018},\\\nobreak{\textit{Freelance}}}

    \begin{itemize}
    \item Built websites using Drupal and WordPress which have collected over 100 sales and leads.
    \item Attended trade shows to gain clients by informing small business owners about SEO and UX.
    \end{itemize}

    \details{\textit{Content Writer $\rightarrow$ Digital Marketing Associate}}{\nobreak{Jun 2016 -- Jul 2018},\\\nobreak{\textit{dLook} / \textit{Jet Digital}}}

    \begin{itemize}
    \item Account service and Salesforce lead management of clients and their digital projects.
    \item Wrote entertainment articles which garnered 500\% more unique views than previous writers.
    \item Also performed technical writing for an array of businesses in various industries.
    \end{itemize}

\end{flushleft}

\vspace{-0.5em}

\hh{Personal Projects}

\begin{flushleft}
    \begin{tabularx}{\textwidth}{X X}
        \hfill\textit{Web App:} & \href{https://gcal.benglitsos.com.au/}{gcal.benglitsos.com.au} \\
        \hfill\textit{Business Information System:} & \href{https://github.com/benjamin-glitsos/inventory-management-system}{github.com/benjamin-glitsos/ims} \\
    \end{tabularx}
\end{flushleft}

\vspace{-0.5em}

\hh{Education}

\begin{flushleft}

    \details{\textit{Bachelor of Commerce Liberal Studies with Marketing \& English majors}}{\nobreak{2014 -- 2018},\\\nobreak{\textit{The University of Sydney}}}

    \begin{itemize}
    \item Distinction average.
    \end{itemize}

\end{flushleft}

\end{document}
